Start by setting the seed of the random number generator so that results
will be reproducible.
```{r}
  set.seed(100) # this is included just to make sure results are reproducible
```

Now I declare a function to simulate a Wright-Fisher model, without mutation.
Note that the WF model assumes that the next generation is formed by sampling with replacement from the current generation, which is easily implemented in R using the function `sample`.

The two parameters are the starting state `x`, and the number of generations to be simulated `ngen`.
```{r}

sim.WF = function(x,ngen){
  for(i in 1:ngen){
    x= sample(x,replace=TRUE)
  }
  return(x)
}
```

To illustrate, here we set up a population of size 20, containing 10 0s and 10 1s, and see the result of evolving it under the WF model for 100 generations.
```{r}
  x0 = c(rep(0,10),rep(1,10)) #starting point is 10 0s and 10 1s
  print(x0)
  y=sim.WF(x0,100)
  print(sort(y))
```

In this case we see that, after 100 generations, everyone is of type `1`. That is the `1` allele went to fixation. How can we compute the probability that the
1 allele will go to fixation in 100 generations? The answer, of course, is to use Monte Carlo: simulate the process many times (in this case 100) and store
the results.

```{r}
  niter=100
  res = matrix(nrow=niter, ncol=length(x0))
  for(i in 1:niter){   
    res[i,]=sim.WF(x0,100)
  }
  res
```

So what proportion of these 100 did the 1 allele go to fixation? To answer
this we have to write a function 'allones' to test whether something is all 1s, and
then use the R function 'apply' to apply this function to test each row of res:
```{r}
  allones = function(x){return(all(x==1))}
  onefixed = apply(res,1,allones)
  onefixed
```

Now we can find the Monte Carlo estimate of the fixation probability as the proportion of our simulations in which 1 became fixed:
```{r}
  mean(onefixed)
```

Of course, we will have some error in this estimate (``Monte Carlo error")!
We can reduce this error by doing more simulations!

```{r}
  niter=10000
  res = matrix(nrow=niter, ncol=length(x0))
  for(i in 1:niter){   
    res[i,]=sim.WF(x0,100)
  }
  onefixed = apply(res,1,allones)
  mean(onefixed)
```





